On the Social Compatibility of Genome Analysis

### 2022-06-16 draft.tex
source ordering

Overall the medical sectors holds much potential for the use of gene testing and therapy, with cheaper and more effective treatment, more reliable diagnoses and

@@

\bibitem{cwduster} Peter A. Chow-White, Troy Duster,
\textbf{Do Health and Forensic DNA Databases Increase Racial Disparities?} (Plos Medicince 2011)

@@

\end{thebibliography}
\end{document}

>>>>

Overall the medical sectors holds much potential for the use of gene testing and therapy, with cheaper and more effective treatment, more reliable diagnoses and hope of a cure for previously terminal disease.

@@

@@

\bibitem{cwduster} Peter A. Chow-White, Troy Duster,
\textbf{Do Health and Forensic DNA Databases Increase Racial Disparities?} (Plos Medicince 2011)
\end{thebibliography}
\end{document}
